\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in diverse fields.  Thus,
  developers have presented various tools for JavaScript programmers, including
  basic interpreters and even linters, compilers, debuggers, and program
  analyzers.  Because such developers treat JavaScript programs as inputs of
  their tools, they desire to deeply understand language semantics and refer to
  ECAM-262, a standard JavaScript language specification written in English.
  However, it is challenging to understand each language feature's possible or
  impossible behaviors by only referring to ECMA-262.  Besides, even if tool
  developers recognize a specific behavior, finding JavaScript programs that
  trigger the behavior is not trivial.

  To alleviate this problem, we present $\tool$, which automatically reduces
  JavaScript language specification with a given \textit{syntactic view}.  A
  syntactic view is a way to indicate which language features tool developers
  want to understand by restricting program syntax and types of evaluation
  results.  Then, our tool automatically reduces ECMA-262 so that it consists of
  only abstract algorithms reachable from a given syntactic view.  Our insight
  is that reachable algorithms represent possible behaviors of each language
  feature.  Furthermore, for each algorithm, our tool automatically finds
  example programs that use the selected language feature and the algorithm in
  Test262, an official JavaScript conformance test suite.  We evaluated $\tool$
  with 177 basic syntactic views and the latest ECMA-262 (ES12 or ES2021),
  including 2,640 algorithms. As a result, our tool reduced ES12 to 30.4
  algorithms with 42.3 Test262 programs for each algorithm in 3.2s on average.
  In addition, we conducted \inred{three} case studies with advanced syntactic
  views to show the practicality of $\tool$.
\end{abstract}
