\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in diverse fields.  However,
  despite its popularity, developers and even JavaScript experts often suffer
  from its highly dynamic and complex nature.  Thus, when they desire to
  understand the detailed semantics of JavaScript, they refer to ECMA-262, the
  standard JavaScript language specification written in English.  However, it is
  challenging to understand all the \textit{possible behaviors} of language
  features by only referring to the specification.  Besides, even if developers
  recognize a possible behavior of a language feature, finding \textit{example
  programs} that trigger the behavior is also not trivial.

  To alleviate this problem, we present $\tool$ for the advanced understanding
  of JavaScript language specification with \textit{syntactic views}. First, we
  introduce syntactic views to help users indicate which language features they
  want to understand by restricting program syntax with type bounds.  Then, for
  a given syntactic view, our tool automatically 1) reduces the call graph
  between abstract algorithms in ECMA-262 to soundly infer possible behaviors
  and 2) searches for example programs that trigger such behaviors in a given
  program pool using their pre-collected execution traces.  For the evaluation
  of $\tool$, we used the latest ECMA-262 (ES13, 2022), including \inred{2,640}
  algorithms, with \inred{18,234} official conformance test programs as the
  search target.  We first evaluated its effectiveness with \inred{177} basic
  syntactic views, and our tool successfully reduced ES13 to \inred{109.4}
  algorithms in \inred{0.8s} and found \inred{42.3} example programs for each
  algorithm in \inred{3.2s} on average.  In addition, we conducted \inred{three}
  case studies with advanced syntactic views to demonstrate the practicality of
  $\tool$.
\end{abstract}
